---
title: "Shopify Data Science Intern Challenge (Question 1)"
author: "Camille Bergeron"
date: "5/2/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# libraries
library(dplyr)
library(tidyverse)
library(knitr)
```

Link to github for these questions: [github](https://github.com/cbergeron2900/Data-Science-Intern-Challenge)

# Question 1

## First Look

```{r}
# looking at data 

# loading the data
orders <- read.csv("2019 Winter Data Science Intern Challenge Data Set - Sheet1.csv")

# avg order value
orders %>%
  select(order_amount) %>%
  summarise(n = mean(order_amount)) %>%
  kable()

# looking at potential outliers
ggplot(orders) +
  geom_boxplot(aes(x = order_amount)) +
  labs(title = "Boxplot of Order Anount", x = "Order Amount")

# extracting the outliers
boxplot.stats(orders$order_amount)$out 

orders[which(orders$order_amount == max(orders$order_amount)), ]
```

The largest outliers are all exactly $704000 by the same user at the same shop with the same payment method. The only difference is that the transactions take place on different days in March, but all at 4:00 am. 

```{r}
# new boxplot without the large order
orders %>%
  filter(user_id != 607) %>%
  ggplot() +
  geom_boxplot(aes(x = order_amount)) +
  labs(title = "Boxplot of Order Anount", x = "Order Amount", subtitle = "With the large outlier removed")
  # there are still lot of outliers so these clearly not it 

# looking at this average 
orders %>%
  filter(user_id != 607) %>%
  summarise(n = mean(order_amount)) %>%
  kable()
# this is much cheaper, so maybe this is better? 

# separating the date and time 
orders <- orders %>%
  separate(created_at, c("date", "time"), " ") %>%
  mutate(date = as.Date(date)) 

# taking out the dates to see if they were closing out 
orders %>%
  filter(shop_id == 42) %>%
  arrange(date) %>%
  head() %>%
  kable()

```

```{r}
# this is the average amount spent on items 
orders %>%
  mutate(avg = order_amount / total_items) %>%
  summarise(n = mean(avg)) %>%
  kable()

```

**Another way to do analysis similar to the average order value (AOV) is by looking at the average value per item. This number is $387 per sneaker. **

